---
title: "Data Visualization"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(tidyverse)
library(readxl)
library(here)
```

### Load data

```{r}
SIDS <- read_excel(here("dataset.xlsx"))
```


* * *

## Part 1: Data
Since the data is obtained randomly, we can generalize the results. The data only provides correlation and not causality since this is an observational study. 

Position( 1-correct position, 0- wrong position)

Risk (1-High Risk, 0-Low Risk)

Heartbeat(100-160 Beats per Min)

Respiratory Rate(25-55 breaths per min)

Temperature(35-37.4 Degree Celcius)

References: https://www.mottchildren.org/health-library/abo2987


* * *


## Part 2: Exploratory data analysis

 
```{r}
ggplot(data = SIDS, aes(x = Number, y = HeartRate)) +
  geom_point()
```

Scatterplot of Various Heartbeats 
 
```{r}
ggplot(data = SIDS, aes(x = Number, y = BodyTemperature )) +
  geom_point()
```

Scatterplot of Various Body Temperatures
```{r}
ggplot(data = SIDS, aes(x = Number, y = RespirationRate  )) +
  geom_point()
```

 Scatterplot of Various Respiration Rates 
```{r}
ggplot(data=SIDS)+ geom_bar(mapping=aes(x=Position))

```

Bar Graph denoting Position Count
```{r}
ggplot(data=SIDS)+ geom_bar(mapping=aes(x=Risk))

```

Bar Graph denoting Risk Count
```{r}
summary(SIDS)
plot(SIDS)

```
* * *

